The Exoplanet Orbit Database \textsc{II}: 2014 updates

### 2014-03-17 draft/ms.tex
Abstract sturcture

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We made an effort to put robustly detected exoplanets together with over 3000 sample of exoplanet candidates (\kepler\ Objects of Interest, KOIs) in the Exoplanet Orbit Database (EOD). The EOD is available at exoplanets.org and we have ZZZ number of confirmed exoplanets as of March 2014.

 Make sure to mention: data are available at exoplanets.org; KOIs are included.
ZZZ Also mention the number of confirmed planets? and maybe the scope of the EOD (what are in our database)
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The Exoplanet Orbit Database (EOD) is

We made an effort to put robustly detected exoplanets together with over 3000 sample of exoplanet candidates (\kepler\ Objects of Interest, KOIs) in the Exoplanet Orbit Database (EOD).

What does our  website go?
The EOD is available at exoplanets.org and we have ZZZ number of confirmed exoplanets as of March 2014.

What has been updated?

 Make sure to mention: data are available at exoplanets.org; KOIs are included.
ZZZ Also mention the number of confirmed planets? and maybe the scope of the EOD (what are in our database)

\end{abstract}
